\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    pdfborderstyle={/S/U/W 0}
}

\titleformat{\section}{\small\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{*1.5}{*0.5}

\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}
\titlespacing*{\subsection}{0pt}{*1}{*0.5}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

\begin{center}
\textbf{\Huge SUYASH SRIJAN}\\[0.5em]
\textbf{\Large ENGINEER}\\[0.5em]
\href{mailto:suyashsrijan@outlook.com}{suyashsrijan@outlook.com} \quad \href{https://suyashsrijan.com}{suyashsrijan.com}
\linebreak\\
\hrulefill\\[0.5em]
\end{center}

\section*{PERSONAL STATEMENT}
As a distinguished iOS Engineer with over 7 years of professional experience, I bring an analytical mindset, product-oriented approach, and a strong passion for creating exceptional iOS applications to the table. My track record of developing successful iOS apps on the App Store is a testament to my skills in creating clean, maintainable and efficient code using Swift. I am a dedicated learner and am always eager to expand my skill set through tailored mentorship and taking on challenging projects. I am a highly motivated individual with the ability to work independently or as part of a cross-functional team, while consistently hitting deadlines. My ultimate goal is to use my skills and experience to create industry-leading products that delight users and make a meaningful impact.

\section*{EXPERIENCE}
\subsection*{Marks and Spencer \hfill April 2023--present}
\textbf{iOS Engineer}
\begin{itemize}[leftmargin=*]
\item Led significant improvements to Sparks, including:
\begin{itemize}
\item Led development of high-impact seasonal campaigns including '12 Days of M\&S' Christmas initiative.
\item Spearheaded complete redesign and architectural overhaul of Sparks hub utilizing the Combine reactive framework, UIKit diffable data sources, and compositional layout.
\item Enhanced existing loyalty functionality through continuous feature improvements and optimizations.
\end{itemize}
\item Drove multiple technical excellence initiatives:
\begin{itemize}
\item Explored and prototyped iOS 18 features including Control Widgets and Apple Intelligence, demonstrating potential improvements through mobile team demos.
\item Enhanced developer experience by integrating OSLog in the app for improved debugging capabilities via Xcode.
\item Resolved critical issues including a crash affecting 20k+ monthly users and restored functionality to a favorite home screen widget.
\item Contributed to successful Xcode 16 migration and resolved potential release blockers.
\end{itemize}
\item Demonstrated technical leadership through weekly iOS meeting facilitation, mentoring junior engineers, and delivering technical presentations.
\item Provided critical production support, including out-of-hours incident resolution for high-priority marketing campaigns.
\end{itemize}

\subsection*{Kin and Carta Europe \hfill June 2018--April 2023}
\textbf{iOS Engineer}
\begin{itemize}[leftmargin=*]
\item Led development of multiple iOS apps across energy, banking, and retail sectors for blue-chip clients (names under NDA), delivering key features including:
\begin{itemize}
\item \textbf{Energy client:} Developed and launched a new app featuring meter readings, tariff switching, and bill viewing, achieving 4.5-star App Store rating with millions of users.
\item \textbf{Banking clients:} Led development teams across three major banking apps, implementing core features like account setup, transaction history, fixed-term deposits, and junior ISAs. Successfully delivered a 5-week app reskin project and collaborated with multiple stakeholders on MVP launch.
\item \textbf{Retail client:} Owned loyalty scheme development over 2 years, implementing digital credit systems and regional expansion, achieving 4.8-star rating with millions of users.
\end{itemize}
\item Collaborated with cross-functional teams to deliver modern iOS experiences utilizing SwiftUI, App Clips, and WidgetKit, incorporating haptic feedback and animations.
\item Enhanced CI/CD workflows by integrating lint/code coverage warnings and automating TestFlight/App Store deployment using Fastlane.
\item Improved product quality through code reviews on GitHub/BitBucket and increased code coverage with unit/integration/snapshot tests.
\item Contributed to engineering excellence through technical presentations, blog posts, and junior engineer mentorship.
\end{itemize}

\subsection*{Double (Dating App) \hfill June--Nov 2015}
\textbf{Android Engineer, Internship}
\begin{itemize}[leftmargin=*]
\item Developed core features of the initial Android app launch, including authentication and main user interface.
\item Contributed to successful iOS-to-Android platform adaptation by providing UX recommendations aligned with Material Design guidelines.
\end{itemize}

\section*{OTHER EXPERIENCE}
\subsection*{Apple \hfill 2018--Now}
\textbf{Open source contributor, Swift}
\begin{itemize}[leftmargin=*]
\item Contributed \href{https://github.com/swiftlang/swift/pulls?q=is:pr+author:theblixguy+is:closed}{100+} compiler improvements including bug fixes and user-facing enhancements.
\item Led implementation of Swift Evolution proposals \href{https://github.com/swiftlang/swift-evolution/blob/main/proposals/0268-didset-semantics.md}{SE-0268} and \href{https://github.com/swiftlang/swift-evolution/blob/main/proposals/0280-enum-cases-as-protocol-witnesses.md}{SE-0280} (featured in WWDC '20), and co-authored \href{https://github.com/swiftlang/swift-evolution/blob/main/proposals/0309-unlock-existential-types-for-all-protocols.md}{SE-0309} (featured in WWDC '22).
\item Member of the \href{https://www.swift.org/contributor-experience-workgroup/}{Swift Contributor Experience workgroup} and featured guest on \href{https://www.swiftcommunitypodcast.org/}{Swift Community Podcast} with Swift creator Chris Lattner.
\end{itemize}

\section*{EDUCATION}
\subsection*{Oxford Brookes University \hfill 2014--2018}
\begin{itemize}[leftmargin=*]
\item Bachelor of Science in Computer Science, Upper Second Class Honours (2:1)
\item Founder and co-organizer of Hack@Brookes, the university's first official hackathon (2016-2017)
\end{itemize}

\section*{SKILLS AND TOOLING}
\begin{itemize}[leftmargin=*]
\item Highly knowledgeable in Swift. Familiar with C/C++, HTML/jS/CSS, Java/Kotlin and Python.
\item Experienced with a wide variety of iOS frameworks and tools, such as UIKit, SwiftUI, CoreAnimation, GCD, Swift Package Manager, Git, Xcode and more. Experienced with various CI systems such as Bitrise, TeamCity and GitHub Actions.
\end{itemize}

\end{document}
